Title Goes Here

### 2020-03-03 analysis/paper/paper.Rmd
edited

  for (i in 1:l) {
    landmarks[i] = list(data.frame(
      read.table(file = data, header=F, skip = LM[i],
                 nrows = nrows[i], col.names = c("X", "Y")),
      IMAGE = as.character(images[i]),
      ID = ID[i],
      SCALE = SCALE[i]))
  }
  do.call(rbind, landmarks) # rbind the list items into a data.frame
}

@@

#Compare multiple artifacts

#Open multiple tps files 
#This will need to be changed to read files inside the project
datadir <- "/Users/gayoungp/CTtps/analysis/data/raw_data/"
files <- dir(datadir, pattern = "*.tps")

>>>>

  for (i in 1:l) {
    landmarks[i] = list(data.frame(
      read.table(file = data, header = F, skip = LM[i],
                 nrows = nrows[i], col.names = c("X", "Y")),
      IMAGE = as.character(images[i]),
      ID = ID[i],
      SCALE = SCALE[i]))
  }
  do.call(rbind, landmarks) # rbind the list items into a data.frame
}

@@

#Compare multiple artifacts 
#Open multiple tps files 
#This will need to be changed to read files inside the project
datadir <- "/Users/gayoungp/CTtps/analysis/data/raw_data/"
files <- dir(datadir, pattern = "*.tps")
